
\appendix     
\part*{Anhang} % Start the appendix part
   
    
\chapter{Anhang} 

\section{POS-Tags}

\begin{longtable}{|l|l|l|}
\caption{Liste aller POS-Tags der Penn Treebank (\cite[vgl.][8]{PENNTREEBANK})}\\
\hline \multicolumn{1}{|c|}{\textbf{ }} & \multicolumn{1}{c|}{\textbf{Tag}} & \multicolumn{1}{c|}{\textbf{Bedeutung}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- Weiterführung}} \\
\hline \multicolumn{1}{|c|}{\textbf{ }} & \multicolumn{1}{c|}{\textbf{Tag}} & \multicolumn{1}{c|}{\textbf{Bedeutung}} \\ \hline 
\endhead

\hline \multicolumn{3}{|r|}{{Weiterführung auf nächster Seite}} \\ \hline
\endfoot

\hline \hline
\endlastfoot
 1. & CC & Coordinating conjunction \\
	 2. & CD & Cardinal number\\
	 3. & DT & Determiner \\
	4.&  EX &	Existential there\\
	5.&	FW &	Foreign word\\
	6.&	IN &	Preposition or subordinating conjunction\\
	7.&	JJ &	Adjective\\
	8.&	JJR &	Adjective, comparative\\
	9.&	JJS &	Adjective, superlative\\
	10.& LS &	List item marker\\
	11.& MD &	Modal\\
	12.& NN &	Noun, singular or mass\\
	13.& NNS &	Noun, plural\\
	14.& NNP &	Proper noun, singular\\
	15.& NNPS &	Proper noun, plural\\
	16.& PDT & Predeterminer\\
	17.& POS & Possessive ending\\
	18. & PRP & Personal pronoun \\
	19.& PRP\$ & Possessive pronoun\\
	20.& RB & Adverb\\
	21.& RBR & Adverb, comparative\\
	22.& RBS & Adverb, superlative\\
	23.& RP & Particle\\
	24.& SYM & Symbol\\
	25.& TO & to\\
	26.& UH & Interjection\\
	27.& VB & Verb, base form\\
	28.& VBD & Verb, past tense\\
	29.& VBG & Verb, gerund or present participle\\
	30.& VBN & Verb, past participle\\
	31.& VBP & Verb, non-3rd person singular present\\
	32.& VBZ & Verb, 3rd person singular present\\
	33.& WDT & Wh-determiner\\
	34.& WP & Wh-pronoun\\
	35.& WP\$ & Possessive wh-pronoun\\
	36.& WRB & Wh-adverb	\\

	  \label{table:POSTAGS}
\end{longtable}



\section{Stanford Dependency-Tags}

\begin{longtable}{|l|l|l|}

  \caption{Liste aller DEP-Tags des Stanford Parsers (\cite[vgl.][3 ff.]{STANFORDDEPS})}\\
\hline \multicolumn{1}{|c|}{\textbf{     }} & \multicolumn{1}{c|}{\textbf{Tag}} & \multicolumn{1}{c|}{\textbf{Bedeutung}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- Weiterführung}} \\
\hline \multicolumn{1}{|c|}{\textbf{     }} & \multicolumn{1}{c|}{\textbf{Tag}} & \multicolumn{1}{c|}{\textbf{Bedeutung}} \\ \hline 
\endhead

\hline \multicolumn{3}{|r|}{{Weiterführung auf nächster Seite}} \\ \hline
\endfoot

\hline \hline
\endlastfoot
  1. & acomp & adjectival complement \\
2. & advcl & adverbial clause modifier\\
3. & advmod & adverb modifier\\
4. & agent & agent\\
5. & amod & adjectival modifier\\
6. & appos & appositional modifier\\
7. & aux & auxiliary\\
8. & auxpass & passive auxiliary\\
9. & cc & coordination\\
10. & ccomp & clausal complement\\
11. & conj & conjunct\\
12. & cop & copula\\
13. & csubj & clausal subject\\
14. & csubjpass & clausal passive subject\\
15. & dep & dependent\\
16. & det & determiner\\
17. & discourse & discourse element\\
18. & dobj & direct object\\
19. & expl & expletive\\
20. & goeswith & goes with\\
21. & iobj & indirect object\\
22. & mark & marker\\
23. & mwe & multi-word expression\\
24. & neg & negation modifier\\
25. & nn & noun compound modifier\\
26. & npadvmod & noun phrase as adverbial modifier\\
27. & nsubj & nominal subject\\
28. & nsubjpass & passive nominal subject\\
29. & num & numeric modifier\\
30. & number & element of compound number\\
31. & parataxis & parataxis\\
32. & pcomp & prepositional complement\\
33. & pobj & object of a preposition\\
34. & poss & possession modifier\\
35. & possessive & possessive modifier\\
36. & preconj & preconjunct\\
37. & predet & predeterminer\\
38. & prep & prepositional modifier\\
39. & prepc & prepositional clausal modifier\\
40. & prt & phrasal verb particle\\
41. & punct & punctuation\\
42. & quantmod & quantifier phrase modifier\\
43. & rcmod & relative clause modifier\\
44. & ref & referent\\
45. & root & root\\
46. & tmod & temporal modifier\\
47. & vmod & reduced non-finite verbal modifier\\
48. & xcomp & open clausal complement\\
49. & xsubj & controlling subject\\

\end{longtable}

\section{Beigabenverzeichnis}
\begin{enumerate}
	\item Seminararbeit
	\begin{enumerate}
		\item Seminararbeit Text2WorldModel.pdf
	\end{enumerate}

\end{enumerate} 

